Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-07 paper/snakemajoranas.tex
use TODO tags
improve the abstract

\date{\today}
\begin{abstract}
We are solving a problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
We do this by introducing a zigzag geometry.
This works because the maximum trajectory length is cut-off due to the geometry and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
In addition to having a large minimum energy gap, the absence of long length trajectories means that the localization length is very short as well.
\end{abstract}

@@

\comment{In a straight system, the Majoranas are very poorly localized.}
For the ribbon system [Fig.~\ref{fig:wavefunctions}(a)], we see that the decay of the density is long compared to the system size.
The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly septated from the next lowest lying eigenstate $E_1$.
Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.  % XXX: probably put the eq for coherence length here?

@@

\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated. % XXX: add ref to Fokko's thesis
Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.

>>>>

\date{\today}
\begin{abstract}
We solve the problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
Trajectories that do not encounter the superconductor for a long time weaken proximity effect in Josephson junctions.
A small induced gap becomes then an important obstacle in creating Majorana states.
We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing robust creation of Majorana states with a gap increased by more than an order of magnitude.
\end{abstract}

@@

\comment{In a straight system, the Majoranas are very poorly localized.}
For the ribbon system [Fig.~\ref{fig:wavefunctions}(a)], we see that the decay of the density is long compared to the system size.
The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is badly septated from the next lowest lying eigenstate $E_1$.
Altogether, the increase in the topological gap, but also the before mentioned reduction of the group velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.  % TODO: probably put the eq for coherence length here?

@@

\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated. % TODO: add ref to Fokko's thesis
Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.
